\section{Conclusion}
\label{sec.conclusion}

The idea of isolating untrusted user applications from the underlying privileged code
to avoid its exploitation by bugs has been realized in different implementations,
but there is no standard method for creating this isolation.
In addition, experience suggests that isolation by itself does not guarantee the security of a system.
%
In this paper, we proposed a new metric based on quantitative measures derived from
the execution of kernel code when running user applications.
We tested the hypothesis that commonly used kernel paths contain fewer bugs.
Using our metric, we generated findings that suggest the hypothesis is reasonable,
 and it become the key principle behind a new design for building secure systems,
which was used to implement a new virtualized security system called Lind. Designed with a minimized
"trusted computing base" (TCB) and interacting only with the kernel in a minimal and safe
way, Lind addresses the need to support riskier system calls by securely
reconstructing complex, yet essential OS functionality inside a sandbox.
%
Evaluation results have shown that Lind is the least likely to trigger historically-reported kernel bugs,
when compared to other virtualization systems, such as VirtualBox, VMWare Workstation, Docker, LXC, 
QEMU, KVM and Graphene.
This suggests that systems using our design are likely to be more secure.

All of the data and source code for this paper is available to other
researchers.  Lind is open source and available at: XXX.  The kernel
trace data can be accessed on the Lind website.  For access
to the kernel exploit code created in this study, please contact the
authors.