\section{Limitations and Future Work}
\label{sec.limitation}

Though Lind shows potential as an effective method for protecting privileged code,
further investigation is required to address issues that were not included in our
initial study.
%We discuss the limitations of Lind in this section.
First, our metric relies on identifying lines of code in the kernel that are
 executed when running applications in secure systems. It is not clear if
 existing hypervisors are small and compact enough to consider all the
 identified paths traversing off executing applications as common paths or
  whether there is still substantial benefit from our metric. \lois{This is a bit
  confusing for several reasons. First, does your perceived limitation come from doing
  the trace while the application is running? Or is the concern that hypervisors
  are too large? Or, for that matter, why are we now talking about hypervisors when
  up front in the paper we establish we are NOT DISCUSSING hypervisors? Please resolve all
  the above.}In %our
future work we will %explore
investigate if the bug metric works well for %operating system virtual machines with a hypervisor.
hypervisor-based VMs.

A second limitation stems from our criteria for determining if a kernel trace is
safe or risky. In our study, the criteria involved checking the trace against a list
 f historical kernel bugs.
  %However, not all bugs can be accurately checked in this manner.
But due to the nature of bugs our proposed metric can not assure if a portion of code
is absolutely a safe or a risky area in kernel.\lois{Doesn't this statement challenge
every claim your paper is making?} For example, bugs that are caused
by a race condition cannot be identified by directly checking if certain lines of
code have been executed. For complicated bugs that involve defects in the internal
kernel data structures, or require complex triggering conditions across multiple
kernel paths, our metric will not be able to accurately determine whether or not
those bugs have been triggered. In such cases, more complex metrics might be needed
 for detection.

%While Lind executes programs like Apache and Tor, it does not
%support every system call or every possible set of arguments. For example,
%symbolic links are not supported.  While the SafePOSIX implementation could
%be extended to do so, we leave this for future work. Also, as mentioned in
%the previous section,


%There were also some avenues we intentionally excluded in this initial
%study that could form the basis for interesting research projects in the
%future. First, we chose not to explore bugs within the applications
%themselves.
%\cappos{move to motivation / threat model.}

Lind has not been optimized for performance, so the results we present here should be taken as a baseline.
%of what is possible.
We would like to explore what existing OS VM optimizations can be safely applied
and what their impact might be.

We would also like to test our metric in other popular operating systems, such as Windows and Mac OS. 
Our experiments were limited to Linux kernel 3.14.1 and some of the typical virtualization systems that existed in Linux. 
It would be interesting
%and beneficial to the advance of secure systems
if similar tests could be run in other widely-used operating systems. In particular, it would be interesting to see if 
having the host and guest VM utilize different operating systems provides better protection. 
\gholami{I dont understand the last sentence.}